BlogForever Crawler: Techniques and Algorithms to Harvest Modern Weblogs

### 2013-11-12 tex/4-techniques.tex
Update readme with gen main.bib instructions.

% The solution
the solution: phjs \cite{readability}
js rendering done upfront, everything else general
screenshot ?

- ez of use vs power, fine because it's automated

>>>>

% The solution
- the solution: phjs
- js rendering done upfront, everything else general
- python scripting click click use case
- ez of use vs power, fine because it's automated
